Accessibility users study: text analysis
========================================================

1. What's in the caption of accessibility users photos? Do they use FB to ask for help with visual problems?

(1) # of question marks?
(2) # of photos with caption
(3) trending words

Example hive query:
/usr/local/prism/bin/hive --namespace mobile -e "select if(accessibility_type = 'voice_over', 1, 0) as label, text as text from test_shaomei_accessibility_sample_user_content_create where content_type = 'photo' and length(text) > 2 and accessibility_type in ('voice_over', 'ios_sample') and privacydata = 40 and locale='en_US';" > onlyfriends_photo_caption_text_ios_vs_vo.tsv

Then run the trend detection algorithm as described in Kleinberg's paper:
python getTrendingTokens.py onlyfriends_photo_caption_text_ios_vs_vo.tsv 30 10 50


Here is the result (positive class is visionally impaired users, negative class for iPhone sample).


normalized absolute change

positive words     |     negative words
------------------ |-------------------
radio | for
to | day
am | and
me | gwen
on | ?
tunein | birthday
listening | happy
with | celebration
by | john
my | have
of | \u2764
the | off
out | it's
peachtree | fun
fm | family
http:\/\/tun.in\/se8qe | work
check | little
hatchi | we
http:\/\/facebook.com\/hatchiapp | beach
you | this
mi | life
\u003c3 | see
his | our
god | miss
first | big
lord | amazing
who | morning
baby | party
eyes | thanks
scrimmage | last
navy\/gold | #tbt
http:\/\/go.bibleinspirationsapp.com\/db_fb | had
was | before
is | awesome
look | na
lol | been
#dailyquote | best
will | vacation
taptapsee | from
http:\/\/bit.ly\/11j2rfj | po
discovered | weekend
take | view
in | lunch
are | dinner
2013 | can't
like | all
pictures | wedding
#picoftheday | tonight
#photooftheday | summer
circus | girl

------------------------------

**normalized relative change**

positive words     |    negative words
------------------ |-------------------
peachtree | raining
taptapsee | #sri_lanka
fm | spiders
http:\/\/tun.in\/sewky | conjuring
lol\udbb8\udf29 | otro
http:\/\/facebook.com\/hatchiapp | truong
karla's | lori
hd2 | hermana
98.7 | kent
#dailyquote | #everybody
blanch | flys
navy\/gold | #feelings
http:\/\/tun.in\/se8qe | #princess
miscellaneous | c\u0169ng
hatchi | #myson
tunein | #ohms
http:\/\/bit.ly\/11j2rfj | miller
radio | snuggles
julian's | tires
circus | snuggled
dengan | #cali
arrowhead | thunder
cane | \udbb9\udfde\udbb9\udfde\udbb9\udfde\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf27\udbb8\udf27\udbb8\udf27\udbb8\udf2c\udbb8\udf2c\udbb8\udf2c\udbba\udf97\udbba\udf97\udbba\udf97\udbb8\udf38\udbb8\udf38\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf33
closely | fingers
scrimmage | lmp
discovered | dialogo
#qotd | avery
listening | jasmine
jeremiah | china
\u266b | hers
elijah | #shorthair
lies | climbed
chester | #exclusively
#camera360# | lml
saya | divide
gabby | explained
\u2026 | replace
yang | #tigers
-* | txt
unlocked | dnt
saving | strike
badge | #aviary
zip | hols
peak | 99
#dope | hermano
champs | 90
checked | #barber101
fellas | #rainyday
philadelphia | blade
dah | locker

-------------------------
**probability change**

positive words     |  negative words
------------------ |-------------------
#truth | yellow
raining | four
#sri_lanka | hanging
woods | lord
spiders | wednesday
conjuring | path
otro | second
truong | hero
lori | aug
hermana | i'm
kent | music
#everybody | therefore
bringing | until
flys | holy
#feelings | relax
#princess | hold
c\u0169ng | want
#myson | turn
#ohms | hot
bill | hoy
tired | #share
miller | beauty
snuggles | keeps
bacon | wind
tires | silver
snuggled | mason
#cali | smh
thunder | #goodnight
\udbb9\udfde\udbb9\udfde\udbb9\udfde\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udc38\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf27\udbb8\udf27\udbb8\udf27\udbb8\udf2c\udbb8\udf2c\udbb8\udf2c\udbba\udf97\udbba\udf97\udbba\udf97\udbb8\udf38\udbb8\udf38\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf33\udbb8\udf33 | heading
fingers | today's
lmp | julian's
#gorgeous | needed
dialogo | listen
avery | tree
jasmine | shower
here | esta
china | boston
cart | \u2764\u2764\u2764
&& | doors
hers | shall
#shorthair | doin
kids | mouth
climbed | camp
#exclusively | came
i'd | cooking
s'mores | baby's
lml | iphone\/ipad
golden | goodnight
divide | result
explained | score




A few keywords pop-out in the caption of photos: **TapTapSee**, and **camera360**.

There are 104 voice_over users and 1 high-contrast-mode users mentioned TapTapSee in their status updates, comment, or photo caption, and none of people in the random sample did so.

I sampled some of the text, it seems that it's a super handy tool for blind people and there are many very moving messages about using it (for example, somebody discovered for the first time that her hair is brown!).

I also looked at the activity trends - nothing concret pop out so far...



2. Does accessibility users write less (status updates) - shorter sentence, less status updates?



```{r}
summary(cars)
```

You can also embed plots, for example:

```{r fig.width=7, fig.height=6}
plot(cars)
```

